---
title: "DataScienceExam3"
author: "JP Reppeto"
date: "7/9/2020"
output: word_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

**1:**
```{r Clear the environment}
rm(list=ls(all=TRUE))
```

**2:**
```{r}
#load tidycensus
library(tidycensus)

#load my API Key
census_api_key("2a948c32a69d16b8ec8ecda67d3076cc9eb6126c")

#load the variables
v10 <- load_variables(year = 2010, dataset = "acs5")
#Used this to locate GINI data by searching "GINI" in view panel (GINI code: B19083_001)

#import state level data for both years
gini10 <- get_acs(geography = "state",
                 variables = c(poverty = c("B19083_001")),
                 year = 2010)

gini15 <- get_acs(geography = "state",
                  variables = c(poverty = c("B19083_001")),
                  year = 2015)

#add year column
gini10$year <- 2010
gini15$year <- 2015

#combine
#load package to deal with these big boys
library(bit64)

#put our data into one big boy panel
library(tidyverse)
inequality_panel = bind_rows(gini10, gini15)

#rename variables
library(data.table)
setnames(inequality_panel, "NAME","state" )
setnames(inequality_panel, "estimate","gini" )

#order
inequality_panel = inequality_panel[order(inequality_panel$state, 
                                          inequality_panel$year), ]

head(inequality_panel)
```

**3-5:**
```{r}
#make it wide by GINI
wide_by_gini <-
  inequality_panel %>%
  pivot_wider(id_cols = c("gini", "year"),
              names_from = c("state", "GEOID"),
              values_from = "gini")

#make it wide by GINI (2)
wide_by_gini <-
  inequality_panel %>%
  pivot_wider(id_cols = c("gini", "year"),
              names_from = "state",
              values_from = "gini")

head(wide_by_gini)


#make it long again
long_inequality <-
  wide_by_gini %>% 
  pivot_longer(cols =starts_with("year"),
               names_to = "year",
               values_to = "gini",
               values_drop_na = FALSE) %>%
  filter(!(current_amount==0))
```
I couldn't get my long_inequality function to work but I would compare the two
with the structure command to see if they have the same number of obersavtions.

**8-9:**

```{R}

#WDI import
library(WDI)
gdp_current = WDI(country = "all", 
                    indicator =c("NY.GDP.MKTP.CD"),
                    start = 2006, end = 2007,
                    extra = FALSE, cache = NULL)

#deflator import
deflator_data = WDI(country = "all", 
                    indicator =c("NY.GDP.DEFL.ZS"),
                    start = 2006, end = 2007,
                    extra = FALSE, cache = NULL)

#rename the deflator variable
library(data.table)
setnames(deflator_data, "NY.GDP.DEFL.ZS", "deflator")
view(deflator_data)

#subset to a USD deflator
usd_deflator = subset(deflator_data, country == "United States")

#merge the two
deflated_data = left_join(gdp_current,
                          usd_deflator,
                          by= "year")

#deflation
deflated_data$deflated_amount = deflated_data$current_amount/
  (deflated_data$deflator/100)
```
code wouldn't work so can't produce a head :/

**10:**
Shiny apps are composed of UI, server, and the front end app itself.

UIs are made of inputs and outputs. Servers are composed of objects that store
your directions and a render function. The front end app is filled by anything
programmed in the UI and processed by the server. 

**11-14:**
```{r}
#pulling Mike's PDF
#loading packages
library(pdftools)
library(tidyr)
library(tidytext)
library(dplyr)
library(stringr)
library(ggplot2)

#pulling up pdf 
mytext=pdf_text(pdf = "https://pdf.usaid.gov/pdf_docs/PA00TNMG.pdf") 

#converting pdf object to df
armeniatext=as.data.frame(mytext)
armeniatext$page=c(1:65)
#renmaing column
colnames(armeniatext)[which(names(armeniatext) == "mytext")] <- "text"

#tokenize/remove stop words
armeniatext=armeniatext %>%
  unnest_tokens(word, text)

armeniatext=armeniatext %>%
anti_join(stop_words)

#frequency analysis for top 6
arfreq <- armeniatext %>%
  count(word, sort = TRUE)

head(arfreq)
```

**15-17:**
```{r}
#load Billboard 100
#packages
library(rvest)
library(dplyr)
library(ggplot2)

#read in the data
hot100 <- "https://www.billboard.com/charts/hot-100"
hot100exam <- read_html(hot100)

#using rvest to find the nodes
#declare the full structure of the webpage to R
body_nodes <- hot100exam %>%
  html_node("body") %>%
  html_children()

body_nodes

#scraping Rank, Artist, Title, Last Week
rank <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
'chart-element__rank__number')]") %>%
  rvest::html_text()

artist <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
'chart-element__information__artist')]") %>%
  rvest::html_text()

title <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
'chart-element__information__song')]") %>%
  rvest::html_text()

lastweek <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
  'chart-element__information__delta__text text--last')]") %>%
  rvest::html_text()

#combine into a df  
chart_df <- data.frame(rank, artist, title, lastweek)

#view as a table
knitr::kable(
  chart_df %>% head(10))
```
